\documentclass[11pt]{article}
%\usepackage{fullpage}
\usepackage{epic}
\usepackage{eepic}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{tikz}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is FULLPAGE.STY by H.Partl, Version 2 as of 15 Dec 1988.
% Document Style Option to fill the paper just like Plain TeX.

\typeout{Style Option FULLPAGE Version 2 as of 15 Dec 1988}

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep

\textheight 8.9in

\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in

\textwidth 6.5in
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{-0.8in}
\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.5in}


\def\ind{\hspace*{0.3in}}
\def\gap{0.1in}
\def\bigap{0.25in}
\newcommand{\Xomit}[1]{}


\begin{document}

\setlength{\parindent}{0in}
\addtolength{\parskip}{0.1cm}
\setlength{\fboxrule}{.5mm}\setlength{\fboxsep}{1.2mm}
\newlength{\boxlength}\setlength{\boxlength}{\textwidth}
\addtolength{\boxlength}{-4mm}
\begin{center}\framebox{\parbox{\boxlength}{{\bf
CS 4820, Spring 2018 \hfill Homework 7, Problem 2}\\
% TODO: fill in your own name, netID, and collaborators
Name: \\
NetID: \\
Collaborators:
}}
\end{center}
\vspace{5mm}

{ \bf (2)} {\em (10 points)}
At Ford-Fulkerson University  there are many 
committees that need to be staffed with professors.  The 
university has $n$ professors organized into $d$ departments;
each professor belongs to only one department.  There are 
$m$ committees, and the following constraints
must be satisfied when staffing the committees.
\begin{enumerate}
\item
The required number of professors on committee $k$ is 
specified by a positive integer $r_k$.
\item
No professor is allowed to serve on more than $c$ committees.
\item
No committee is allowed to have more than one professor
from the same department.
\item
For each professor $j$, there is a list $L_j$ of the 
committees on which he or she is qualified to serve.  
Professor $j$ is not allowed to serve on committee $k$
unless $k \in L_j$.
\end{enumerate}
Design a polynomial-time algorithm to determine whether 
it is possible to staff each committee
without violating any of the constraints listed above.
If it is possible to staff the committees, your algorithm should output an
assignment of professors to committees that satisfies
all of the constraints.  The input to the problem
is specified by the numbers $n,d,m, r_1,\ldots,r_m$,
and the lists $L_1,\ldots,L_n$.


\vskip \bigap

%% Your solution goes here.

\end{document}
