\documentclass[11pt]{article}
%\usepackage{fullpage}
\usepackage{epic}
\usepackage{eepic}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{tikz}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is FULLPAGE.STY by H.Partl, Version 2 as of 15 Dec 1988.
% Document Style Option to fill the paper just like Plain TeX.

\typeout{Style Option FULLPAGE Version 2 as of 15 Dec 1988}

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep

\textheight 8.9in

\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in

\textwidth 6.5in
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{-0.8in}
\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.5in}


\def\ind{\hspace*{0.3in}}
\def\gap{0.1in}
\def\bigap{0.25in}
\newcommand{\Xomit}[1]{}


\begin{document}

\setlength{\parindent}{0in}
\addtolength{\parskip}{0.1cm}
\setlength{\fboxrule}{.5mm}\setlength{\fboxsep}{1.2mm}
\newlength{\boxlength}\setlength{\boxlength}{\textwidth}
\addtolength{\boxlength}{-4mm}
\begin{center}\framebox{\parbox{\boxlength}{{\bf
CS 4820, Spring 2018 \hfill Homework 8, Problem 1}\\
% TODO: fill in your own name, netID, and collaborators
Name: \\
NetID: \\
Collaborators:
}}
\end{center}
\vspace{5mm}

{ \bf (1)} {\em (8 points)}
At Cornell University, doctoral students in Computer Science
can earn their Ph.D.\ either in Ithaca or at the new Cornell Tech
campus in New York City. However all students initiate their 
study in Ithaca and complete some course requirements 
before potentially moving to New York City. This inspires
the following course scheduling problem.

A department has $p$ professors and $2p$ courses. Each
professor teaches two courses, one per semester. Assume 
that professors are numbered $0,\ldots,p-1$ and courses
are numbered $0,\ldots,2p-1$ such that professor $i$
teaches courses $2i$ and $2i+1$, for each $i=0,\ldots,p-1$.
There are $s$ students (numbered $0,\ldots,s-1$)
each of whom is trying
to finish their remaining course requirements in the fall semester
so that they can move to a different campus in the spring. 
The remaining course requirements for student $j$ are fulfilled by 
taking at least $n(j)$ courses from a specified list 
$L(j)$. 

The {\sc Impatient Grad Students Problem (IGSP)} is the
following decision problem: given the numbers $p,s,
n(0),\ldots,n(s-1)$ (in binary) and the lists $L(0),\ldots,L(s-1)$,
decide whether the courses can partitioned into the 
fall and spring semesters such that
\begin{compactenum}
\item each professor teaches one fall course and one spring course
\item for each list $L(j)$, at least $n(j)$ of the courses in $L(j)$ 
  are scheduled in the fall semester.
\end{compactenum}
Prove that {\sc IGSP} is NP-complete.

\vskip \bigap

%% Your solution goes here.

\end{document}
